\documentclass{amsart}
\usepackage{hyperref,amsmath,amsfonts}

\begin{document}
\title{Library for Quadratic Programming}
\author{Vojt\v{e}ch Franc\\ xfrancv at cmp.felk.cvut.cz} 
\maketitle
%\tableofcontents

\def\x{\mathbf x}
\def\f{\mathbf f}
\def\a{\mathbf a}
\def\H{\mathbf H}
\def\Sequ{\rm S_{\rm equ}}
\def\Sneq{\rm S_{\rm neq}}
\renewcommand{\Re}{\mathbb{R}}

\section*{Introduction}

LIBQP is C library which implements algorithms for solving two special instances of
convex Quadratic Programming (QP):

%\begin{enumerate}
 % \item 

\large
\subsection*{QP task with simplex constraints} This QP task is defined as follows
\[
   \begin{array}{lrcll}
     \mbox{minimize} &\multicolumn{4}{l}{\displaystyle\frac{1}{2}\x^T \H \x +
       \x^T \f} \\ \\
     \mbox{subject to} 
     & \displaystyle\sum_{i\in I_k} x_i & = & b_k\:, & k\in \Sequ \\ 
     & \displaystyle\sum_{i\in I_k} x_i & \leq & b_k\:, & k\in \Sneq \\
     & x_i & \geq & 0\:, & i\in I \:.
   \end{array}
\]
where \(\x = (x_1,\ldots,x_n)\in\Re^n\) is the optimized vector, \(\H
\in\Re^{n\times n}\) is a symmetric positive semi-definite matrix,
\(\f\in\Re^n\) is a vector, \(I =
\{1,\ldots,n\}\) is an index set, \(\{I_1,\ldots,I_m\}\) are subsets of \(I\)
such that  \(I_1\cup \ldots \cup I_k = I\) and \(I_1 \cap \ldots \cap I_k =
\emptyset\), \(\Sequ\) and \(\Sneq\) are index sets such that  
\(\Sequ \cup \Sneq = \{1,\ldots,m\}\) and \(\Sequ \cap \Sneq = \emptyset\),
\((b_1,\ldots,b_m)\in\Re^m\) are positive numbers.


The implemented solver (\verb|libqp_splx.c|) is a generalization of the method
proposed in~\cite{Franc-TR-2006-04,Fan-JMLR05}. It is based on the Sequential Minimal
Optimization (SMO) algorithm with an improved working set selection
strategy. Solving instances of this QP task is required, for example, in machine 
learning methods like Structured SVM learning, Bundle Methods for Risk
Minimization, binary SVM with L2-soft margin, etc. 

\subsection*{QP task with box constraints and a single linear equality constraint}
This QP task is defined as follows
\[
  \begin{array}{lrcl}
    \mbox{minimize} &\multicolumn{3}{l}{\displaystyle\frac{1}{2}\x^T \H \x +
      \x^T \f} \\ \\
    \mbox{subject to} 
    & \displaystyle\x^T \a & = & b\:, \\ 
    & \multicolumn{3}{c}{\displaystyle l_i \leq x_i \leq u_i\:, \qquad i=1,\ldots,n}\:,
  \end{array}
\]
where \(\x = (x_1,\ldots,x_n)\in\Re^n\) is the optimized vector, \(\H
\in\Re^{n\times n}\) is a symmetric positive semi-definite matrix,
\(\f\in\Re^n\) is a vector, $\a\in\Re^n$ is a vector with non-zero entries,
$b\in\Re$ is a scalar, $(l_1,\ldots,l_n)\in(\Re \cup \{-\infty\})^n$ and
$(u_1,\ldots,u_n)\in(\Re\cup\{\infty\})^n$ are lower and upper bounds,
respectively. 

The solver (\verb|libqp_gsmo.c|) is the exact implementation of the 
Generalized Sequential Minimal Optimizer proposed in~\cite{Keerthi-00}.
Solving this QP task is required, for example, when training binary 
SVM with L1-soft margin. 

\section*{Interfaces}

LIBQP is implemented in C language and interfaces to Matlab.

\section*{Platforms}

GNU/Linux. It should run also under Windows though not tested.

\section*{Installation}

LIBQP can be downloaded from \url{http://cmp.felk.cvut.cz/~xfrancv/libqp/libqp.zip}.

\subsection*{MATLAB}

\begin{enumerate}
  \item Run Matlab and go to the folder \verb|libqp_root/matlab|
    \begin{verbatim}
      cd libqp_root/matlab
    \end{verbatim}
  \item Compile mex files by running
    \begin{verbatim}
      libqp_compile
    \end{verbatim}
\end{enumerate}
Now you can use \verb|libqp_splx| and \verb|libqp_gsmo| solvers located in
\verb|libqp_root/matlab|. To make these function visible from Matlab you 
need to add 
\begin{verbatim}
    addpath('libqp_root/matlab')
\end{verbatim}
to your \verb|startup.m| file. 

\noindent
To test the solvers run scripts
\begin{verbatim}
  libqp_splx_test
  libqp_gsmo_test
\end{verbatim}


\subsection*{Example application}

\begin{enumerate}
  \item Go to the folder \verb|libqp_root/examples|
    \begin{verbatim}      
      cd libqp_root/examples
    \end{verbatim}
  \item Issue make 
    \begin{verbatim}      
      make
    \end{verbatim}
\end{enumerate}
Now you can run test script
\begin{verbatim}      
    ./run_test
\end{verbatim}


\section*{License}

LIBQP is licensed under the GPL version 3 (\url{http://gplv3.fsf.org/}).


\begin{thebibliography}{00}
\bibitem[1]{Franc-TR-2006-04}
V. Franc, V. Hlavac. A Novel Algorithm for Learning Support Vector Machines
with Structured Output Spaces. Research Report K333 22/06, CTU-CMP-2006-04. 
May, 2006. 
\url{ftp://cmp.felk.cvut.cz/pub/cmp/articles/franc/Franc-TR-2006-04.ps}
\bibitem[2]{Fan-JMLR05}
R.-E. Fan, P.-H. Chen, C.-J. Lin. Working Set Selection Using Second Order 
Information for Training SVM. JMLR. vol 6. 2005.
\url{TBA}
\bibitem[3]{Keerthi-00}
S.-S. Keerthi, E.G.Gilbert. Convergence of a Generalized SMO Algorithm for SVM 
Classifier Design. Technical Report CD-00-01, Control Division, Dept. of Mechanical 
and Production Engineering, National University of Singapore, 2000. 
\url{http://citeseer.ist.psu.edu/keerthi00convergence.html}
\end{thebibliography}
\end{document}
